---
title: "FARS - Summarizing & Visualizing the Fatality Accident Reporting System"
author: "John Christensen"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Introduction

There are two things you can do with the fars package:

1. You can summarize car accident fatality counts by year & month using the `fars_summarize_years()` function
2. You can visualize car accident fatalities within a state & year using the `fars_map_state()` function

## Summarize accident fatalities by year  & month using `fars_summarize_years()`

To summarize car accident fatalities by year, using the `fars_summarize_years()` function, supply a year or vector of years between 2013-2015: 

```{r}
library(fars)
fars_summarize_years(c(2013, 2014, 2015))
```


## Visualize accident fatalities within a state & year using `fars_map_state()`

To visualize car accident fatalities within a state & year using the `fars_map_state()` function, supply a single state code and single year between 2013-2015:

```{r}
fars_map_state(48, 2015)
```

FARS state codes can be downloaded [here](https://www.gsa.gov/reference/geographic-locator-codes/glcs-for-the-us-and-us-territories).
